Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Added demographics

>>>>

\subsubsection{Demographic Factors}

We observed that participants' responses to our scenarios were correlated with several demographic factors. First, we observed that by far the biggest factor in participants' decisions to rate a scenario as very upsetting was their self-reported general privacy concern level, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a large statistically significant effect when comparing average IUIPC scores with the fraction of scenarios that each participant reported as being very upsetting ($\rho=0.446$, $p<0.0005$). Similarly, we observed that age was also a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the age effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$), as others have also observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs. 60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender. Finally, we observed no correlation between education level and VUR.
